---
title: "Supplementary results"
output:
  html_document:
    code_download: true
    code_folding: hide
    toc: true
    toc_float:
      collapsed: true
---

# Setup

```{r libraries}
library(tidyverse)
library(here)
library(kableExtra)

library(glmmTMB)
library(broom.mixed)

library(tidygraph)
library(ggraph)
```

```{r custom-functions}
source(here("code", "utils", "ggplot_themes.R"))
source(here("code", "utils", "modeling_utils.R"))
source(here("code", "utils", "representation_utils.R"))
source(here("code", "utils", "unicode_greek.R"))

# One-off utils (i.e., written for this script, not general-purpose)
predict_glmmTMB <- function(make_predictions_for, model_object) {
  make_predictions_for %>%
    bind_cols(
      predict(
        object = model_object,
        newdata = .,
        re.form = NA, allow.new.levels = TRUE, se.fit = TRUE, type = "response"
      )
    )
}

check_significance <- function(tidy_df) {
  tidy_df %>%
    mutate(
      sig = case_when(
        p.value < 0.001 ~ "***",
        p.value < 0.01 ~ "**",
        p.value < 0.05 ~ "*",
        p.value < 0.1 ~ ".",
        TRUE ~ ""
      )
    )
}
```

```{r knitting-setup}
# To control when to save figures
knitting <- knitr::is_html_output()

if (knitting) {
  if (!dir.exists(here("figures"))) {
    dir.create(here("figures"))
  }
}
```


# Memory accuracy

```{r load-memory-data}
mem_study1 <- here("data", "clean-data", "study1_memory.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  mutate(study = "Study 1", measurement_id = str_c("D", measurement_id)) %>%
  filter(from != to)

mem_study2 <- here("data", "clean-data", "study2_memory.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  mutate(study = "Study 2", measurement_id = str_c("D", measurement_id)) %>%
  filter(from != to)

mem_study3 <- here("data", "clean-data", "study3_memory.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  mutate(
    study = "Study 3",
    measurement_id = case_when(
      measurement_id == 1 ~ "D1",
      measurement_id == 2 ~ "D1b",
      measurement_id == 3 ~ "D2"
    )
  ) %>%
  filter(from != to)
```

## Study 1

We'll start with study 1. Since this is a one-day study, we're only interested in testing memory accuracy against chance (50%).

```{r memory-study1}
stats_mem_study1 <- mem_study1 %>%
  glmmTMB(
    correct ~ 1 + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_mem_study1 %>%
  tidy() %>%
  kbl(
    caption = str_c(
      "<center>", "Memory: Study 1", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive"))
```

## Study 2

Study 2 was a two-day study, so we'll test how accuracy changes after overnight rest.

```{r memory-study2}
stats_mem_study2 <- mem_study2 %>%
  glmmTMB(
    correct ~ measurement_id + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_mem_study2 %>%
  tidy() %>%
  kbl(
    caption = str_c(
      "<center>", "Memory: Study 2", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive"))
```

## Study 3

For the primary analysis of interest, we can analyze study 3 just like we analyzed study 2.

```{r memory-study3-overnight}
stats_mem_study3_overnight_rest <- mem_study3 %>%
  filter(measurement_id %in% c("D1", "D2")) %>%
  glmmTMB(
    correct ~ measurement_id + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_mem_study3_overnight_rest %>%
  tidy() %>%
  kbl(
    caption = str_c(
      "<center>", "Memory: Study 3, overnight rest", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive"))
```

Study 3 also included an awake rest condition at the end of Day 1. We'll make "after awake rest" the reference category and compare it against the other measurements (before/after overnight rest).

```{r memory-study3-awake}
stats_mem_study3_awake_rest <- mem_study3 %>%
  mutate(measurement_id = fct_relevel(measurement_id, "D1b")) %>%
  glmmTMB(
    correct ~ measurement_id + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_mem_study3_awake_rest %>%
  tidy() %>%
  kbl(
    caption = str_c(
      "<center>", "Memory: Study 3, awake rest", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive"))
```


# Navigation accuracy

```{r load-navigation-data}
nav_study1 <- here("data", "clean-data", "study1_message_passing.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    two_correct_options == FALSE,
    shortest_path_given_opts == shortest_path_given_start_end
  ) %>%
  mutate(
    study = "Study 1",
    measurement_id = str_c("D", measurement_id),
    shortest_path = factor(shortest_path_given_opts)
  ) %>%
  select(
    study, sub_id, measurement_id, shortest_path,
    startpoint_id, endpoint_id,
    opt1_id, opt2_id,
    correct_choice, sub_choice,
    correct, rt
  )

nav_study2 <- here("data", "clean-data", "study2_message_passing.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    two_correct_options == FALSE,
    shortest_path_given_opts == shortest_path_given_start_end
  ) %>%
  mutate(
    study = "Study 2",
    measurement_id = case_when(
      network == "learned" ~ str_c("D", measurement_id),
      network == "reevaluated" ~ "D2b"
    ),
    shortest_path = factor(shortest_path_given_opts)
  ) %>%
  select(
    study, sub_id, measurement_id, shortest_path,
    startpoint_id, endpoint_id,
    opt1_id, opt2_id,
    correct_choice, sub_choice,
    correct, rt
  )

nav_study3 <- here("data", "clean-data", "study3_message_passing.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    two_correct_options == FALSE,
    shortest_path_given_opts == shortest_path_given_start_end
  ) %>%
  mutate(
    study = "Study 3",
    measurement_id = case_when(
      network == "reevaluated" ~ "D2b",
      measurement_id == 1 ~ "D1",
      measurement_id == 2 ~ "D1b",
      measurement_id == 3 ~ "D2"
    ),
    shortest_path = factor(shortest_path_given_opts)
  ) %>%
  select(
    study, sub_id, measurement_id, shortest_path,
    startpoint_id, endpoint_id,
    opt1_id, opt2_id,
    correct_choice, sub_choice,
    correct, rt
  )
```

## Navigation before overnight rest

We want to know whether navigation accuracy is different from chance at each distance, so we'll iteratively reparameterize the model so that each distance is the reference category.

We'll start with study 1. Note that estimating a random slope leads to model convergence problems in studies 2-3, so we'll only be estimating a random intercept per subject.

```{r nav-day1-study1}
stats_nav_study1_dist2 <- nav_study1 %>%
  mutate(shortest_path = fct_relevel(shortest_path, "2")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study1_dist3 <- nav_study1 %>%
  mutate(shortest_path = fct_relevel(shortest_path, "3")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study1_dist4 <- nav_study1 %>%
  mutate(shortest_path = fct_relevel(shortest_path, "4")) %>%
  glmmTMB(
    correct ~ shortest_path + (1  | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_study1_dist2,
    "dist-3" = stats_nav_study1_dist3,
    "dist-4" = stats_nav_study1_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: Day 1, Study 1", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 4) %>%
  pack_rows("Ref. Cat. dist-3", 5, 8) %>%
  pack_rows("Ref. Cat. dist-4", 9, 12)
```

Moving on to study 2:

```{r nav-day1-study2}
stats_nav_study2_day1_dist2 <- nav_study2 %>%
  filter(measurement_id == "D1") %>%
  mutate(shortest_path = fct_relevel(shortest_path, "2")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study2_day1_dist3 <- nav_study2 %>%
  filter(measurement_id == "D1") %>%
  mutate(shortest_path = fct_relevel(shortest_path, "3")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study2_day1_dist4 <- nav_study2 %>%
  filter(measurement_id == "D1") %>%
  mutate(shortest_path = fct_relevel(shortest_path, "4")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_study2_day1_dist2,
    "dist-3" = stats_nav_study2_day1_dist3,
    "dist-4" = stats_nav_study2_day1_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: Day 1, Study 2", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 4) %>%
  pack_rows("Ref. Cat. dist-3", 5, 8) %>%
  pack_rows("Ref. Cat. dist-4", 9, 12)
```

And finally study 3:

```{r nav-day1-study3}
stats_nav_study3_day1_dist2 <- nav_study3 %>%
  filter(measurement_id == "D1") %>%
  mutate(shortest_path = fct_relevel(shortest_path, "2")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study3_day1_dist3 <- nav_study3 %>%
  filter(measurement_id == "D1") %>%
  mutate(shortest_path = fct_relevel(shortest_path, "3")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study3_day1_dist4 <- nav_study3 %>%
  filter(measurement_id == "D1") %>%
  mutate(shortest_path = fct_relevel(shortest_path, "4")) %>%
  glmmTMB(
    correct ~ shortest_path + (1 | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_study3_day1_dist2,
    "dist-3" = stats_nav_study3_day1_dist3,
    "dist-4" = stats_nav_study3_day1_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: Day 1, Study 3", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 4) %>%
  pack_rows("Ref. Cat. dist-3", 5, 8) %>%
  pack_rows("Ref. Cat. dist-4", 9, 12)
```


## Navigation after overnight rest

In studies 2-3, subjects returned to the lab after overnight rest. The primary analysis of interest is to test whether there is evidence of navigation accuracy increasing. Because we're interested in addressing this question for each distance, we'll be iteratively reparameterizing the models so that each distance is the reference category.

```{r nav-day2-study2}
stats_nav_study2_day2_dist2 <- nav_study2 %>%
  filter(measurement_id %in% c("D1", "D2")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "2")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study2_day2_dist3 <- nav_study2 %>%
  filter(measurement_id %in% c("D1", "D2")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "3")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study2_day2_dist4 <- nav_study2 %>%
  filter(measurement_id %in% c("D1", "D2")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "4")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_study2_day2_dist2,
    "dist-3" = stats_nav_study2_day2_dist3,
    "dist-4" = stats_nav_study2_day2_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: Day 2, Study 2", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 9) %>%
  pack_rows("Ref. Cat. dist-3", 10, 18) %>%
  pack_rows("Ref. Cat. dist-4", 19, 27)
```

We'll do the same for study 3.

```{r nav-day2-study3}
stats_nav_study3_day2_dist2 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D2")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "2")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study3_day2_dist3 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D2")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "3")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study3_day2_dist4 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D2")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "4")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_study3_day2_dist2,
    "dist-3" = stats_nav_study3_day2_dist3,
    "dist-4" = stats_nav_study3_day2_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: Day 2, Study 3", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 9) %>%
  pack_rows("Ref. Cat. dist-3", 10, 18) %>%
  pack_rows("Ref. Cat. dist-4", 19, 27)
```

## Navigation after awake rest

In study 3, we tested whether a brief period of awake rest was sufficient for improving navigation accuracy.

```{r nav-awake-rest}
stats_nav_awake_rest_dist2 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D1b")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "2")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path +
      (1 + measurement_id + shortest_path | sub_id),
    family = binomial,
    data = .
  )

stats_nav_awake_rest_dist3 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D1b")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "3")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path +
      (1 + measurement_id + shortest_path | sub_id),
    family = binomial,
    data = .
  )

stats_nav_awake_rest_dist4 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D1b")) %>%
  mutate(shortest_path = fct_relevel(shortest_path, "4")) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path +
      (1 + measurement_id + shortest_path | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_awake_rest_dist2,
    "dist-3" = stats_nav_awake_rest_dist3,
    "dist-4" = stats_nav_awake_rest_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: After awake rest", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 16) %>%
  pack_rows("Ref. Cat. dist-3", 17, 32) %>%
  pack_rows("Ref. Cat. dist-4", 33, 48)
```

## Navigation after reevaluation

In studies 2-3, we tested for evidence of cached representations using a transition reevaluation paradigm.

We'll start by looking at study 2...

```{r nav-tr-study2}
stats_nav_study2_tr_dist2 <- nav_study2 %>%
  mutate(
    shortest_path = fct_relevel(shortest_path, "2"),
    measurement_id = fct_relevel(measurement_id, "D2b")
  ) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study2_tr_dist3 <- nav_study2 %>%
  mutate(
    shortest_path = fct_relevel(shortest_path, "3"),
    measurement_id = fct_relevel(measurement_id, "D2b")
  ) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study2_tr_dist4 <- nav_study2 %>%
  mutate(
    shortest_path = fct_relevel(shortest_path, "4"),
    measurement_id = fct_relevel(measurement_id, "D2b")
  ) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_study2_tr_dist2,
    "dist-3" = stats_nav_study2_tr_dist3,
    "dist-4" = stats_nav_study2_tr_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: Reevaluation, Study 2", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 15) %>%
  pack_rows("Ref. Cat. dist-3", 16, 30) %>%
  pack_rows("Ref. Cat. dist-4", 31, 45)
```

And we'll do the same for study 3...

```{r nav-tr-study3}
stats_nav_study3_tr_dist2 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D2", "D2b")) %>%
  mutate(
    shortest_path = fct_relevel(shortest_path, "2"),
    measurement_id = fct_relevel(measurement_id, "D2b")
  ) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study3_tr_dist3 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D2", "D2b")) %>%
  mutate(
    shortest_path = fct_relevel(shortest_path, "3"),
    measurement_id = fct_relevel(measurement_id, "D2b")
  ) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

stats_nav_study3_tr_dist4 <- nav_study3 %>%
  filter(measurement_id %in% c("D1", "D2", "D2b")) %>%
  mutate(
    shortest_path = fct_relevel(shortest_path, "4"),
    measurement_id = fct_relevel(measurement_id, "D2b")
  ) %>%
  glmmTMB(
    correct ~ measurement_id * shortest_path + (1 + measurement_id | sub_id),
    family = binomial,
    data = .
  )

map_dfr(
  .x = list(
    "dist-2" = stats_nav_study3_tr_dist2,
    "dist-3" = stats_nav_study3_tr_dist3,
    "dist-4" = stats_nav_study3_tr_dist4
  ),
  .f = ~tidy(.x, conf.int = TRUE),
  .id = "ref_cat"
) %>%
  check_significance() %>%
  select(-c(group, ref_cat, effect, component)) %>%
  kbl(
    caption = str_c(
      "<center>", "Navigation accuracy: Reevaluation, Study 3", "</center>"
    ),
    digits = 3
  ) %>%
  kable_styling(bootstrap_options = c("responsive")) %>%
  pack_rows("Ref. Cat. dist-2", 1, 15) %>%
  pack_rows("Ref. Cat. dist-3", 16, 30) %>%
  pack_rows("Ref. Cat. dist-4", 31, 45)
```


## Navigation problems with two correct answers

There were some trials where both Sources had equivalent shortest path distances from the Target. Here, we do an "item analysis" style analysis to see how different agents (humans, BFS, SR) solve these problems. Note that these are "held-out" trials, i.e., that they were not used to estimate parameters.

Because the unit of analysis are items (i.e., trials), rather than subjects, we'll pool over all studies here.

### Load data

```{r load-tie-data}
nav_study1_ties <- here("data", "clean-data", "study1_message_passing.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    two_correct_options == TRUE,
    shortest_path_given_opts == shortest_path_given_start_end
  ) %>%
  mutate(
    study = "Study 1",
    measurement_id = str_c("D", measurement_id),
    shortest_path = factor(shortest_path_given_opts)
  ) %>%
  select(
    study, sub_id, measurement_id, shortest_path,
    startpoint_id, endpoint_id,
    opt1_id, opt2_id,
    correct_choice, sub_choice,
    correct, rt
  ) %>%
  filter(measurement_id %in% c("D1", "D2"))

nav_study2_ties <- here("data", "clean-data", "study2_message_passing.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    two_correct_options == TRUE,
    shortest_path_given_opts == shortest_path_given_start_end
  ) %>%
  mutate(
    study = "Study 2",
    measurement_id = case_when(
      network == "learned" ~ str_c("D", measurement_id),
      network == "reevaluated" ~ "D2b"
    ),
    shortest_path = factor(shortest_path_given_opts)
  ) %>%
  select(
    study, sub_id, measurement_id, shortest_path,
    startpoint_id, endpoint_id,
    opt1_id, opt2_id,
    correct_choice, sub_choice,
    correct, rt
  ) %>%
  filter(measurement_id %in% c("D1", "D2"))

nav_study3_ties <- here("data", "clean-data", "study3_message_passing.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    two_correct_options == TRUE,
    shortest_path_given_opts == shortest_path_given_start_end
  ) %>%
  mutate(
    study = "Study 3",
    measurement_id = case_when(
      network == "reevaluated" ~ "D2b",
      measurement_id == 1 ~ "D1",
      measurement_id == 2 ~ "D1b",
      measurement_id == 3 ~ "D2"
    ),
    shortest_path = factor(shortest_path_given_opts)
  ) %>%
  select(
    study, sub_id, measurement_id, shortest_path,
    startpoint_id, endpoint_id,
    opt1_id, opt2_id,
    correct_choice, sub_choice,
    correct, rt
  ) %>%
  filter(measurement_id %in% c("D1", "D2"))
```

```{r load-comp-model-data}
params <- here("data", "param-fits", "clean_param_fits.csv") %>%
  read_csv(show_col_types = FALSE)

adjlist <- here("data", "clean-data", "adjlist_learned.csv") %>%
  read_csv(show_col_types = FALSE)
```

### SR PPC

To look at the SR model predictions, we need to simulate subject-specific SRs, given their estimated parameters.

```{r simulate-observations}
set.seed(sum(utf8ToInt("Jenny and me was like peas and carrots")))

simulated_paired_associates <- adjlist %>%
  filter(edge == 1) %>%
  select(from, to) %>%
  expand_grid(set = 1:5000, .) %>%
  group_by(set) %>%
  slice_sample(prop = 1) %>%
  ungroup()
```

```{r ppc-sr}
ppc_sr_matrix <- params %>%
  filter(model == "sr") %>%
  select(
    study, sub_id, measurement_id, name = param_name, value = param_value
  ) %>%
  pivot_wider() %>%
  group_by(study, sub_id, measurement_id) %>%
  nest() %>%
  mutate(
    sim_sr = map(
      .x = data,
      .f = ~build_rep_sr(
        learning_data = simulated_paired_associates %>% filter(set %in% 1:100),
        this_alpha = 0.1,
        this_gamma = .x$sr_gamma,
        bidirectional = TRUE
      )
    )
  ) %>%
  unnest(sim_sr) %>%
  unnest(data) %>%
  ungroup()
```

### Item analysis

Here, we're basically just looking at the probability of choosing Source A over Source B.

```{r ties-human}
tie_item_analysis_humans <- bind_rows(
  nav_study1_ties, nav_study2_ties, nav_study3_ties
) %>%
  group_by(
    measurement_id, shortest_path, startpoint_id, endpoint_id, opt1_id, opt2_id
  ) %>%
  summarise(
    p_human_opt1 = mean(sub_choice == opt1_id),
    .groups = "drop"
  )
```

```{r ties-bfs}
# Basically an asymptotic BFS agent
bfs_avg_accuracy_ties <- here("data", "bfs-sims", "bfs_sims_learned.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    two_correct_options == TRUE,
    shortest_path_given_opts == shortest_path_given_start_end
  ) %>%
  mutate(shortest_path = factor(shortest_path_given_opts)) %>%
  select(
    shortest_path, startpoint_id, endpoint_id, opt1_id, opt2_id,
    bfs_choice, bfs_correct_choice, bfs_n_visits_total
  ) %>%
  group_by(shortest_path, startpoint_id, endpoint_id, opt1_id, opt2_id) %>%
  summarise(
    p_bfs_opt1 = mean(bfs_choice == opt1_id),
    bfs_visits = mean(bfs_n_visits_total),
    .groups = "drop"
  )

# BFS agent that is informed by subject-specific estimated parameters
tie_item_analysis_bfs <- bind_rows(
  nav_study1_ties, nav_study2_ties, nav_study3_ties
) %>%
  left_join(
    params %>%
      filter(model == "bfs") %>%
      pivot_wider(names_from = param_name, values_from = param_value) %>%
      select(study, sub_id, measurement_id, search_threshold, lapse_rate)
  ) %>%
  left_join(bfs_avg_accuracy_ties) %>%
  mutate(
    p_sub_choice_bfs = if_else(
      sub_choice == opt1_id,
      p_bfs_opt1,
      1 - p_bfs_opt1
    )
  ) %>%
  select(-p_bfs_opt1) %>%
  # What's the probability of *completing* BFS-online all the way through?
  rowwise() %>%
  mutate(
    search_threshold = search_threshold,
    p_complete_bfs = softmax(
      option_values = c(search_threshold, bfs_visits),
      option_chosen = 1,
      temperature = 1
    )
  ) %>%
  ungroup() %>%
  # Weigh BFS predictions accordingly
  mutate(
    p_give_up = 1 - p_complete_bfs,
    p_bfs_opt1 = (p_complete_bfs * p_sub_choice_bfs) + (p_give_up * 1/2),
    ### Add lapse rate
    #   Dividing by 2 is because there are two options to choose from
    #   Therefore, when lapse rate = 1, this becomes chance = 1/2
    p_bfs_opt1 = p_bfs_opt1 * (1-lapse_rate) + (lapse_rate/2)
  ) %>%
  # Average over trials
  group_by(
    measurement_id, shortest_path, startpoint_id, endpoint_id, opt1_id, opt2_id
  ) %>%
  summarise(
    p_bfs_opt1 = mean(p_bfs_opt1),
    .groups = "drop"
  )
```

```{r ties-sr}
tie_item_analysis_sr <- bind_rows(
  nav_study1_ties, nav_study2_ties, nav_study3_ties
) %>%
  left_join(
    ppc_sr_matrix %>%
      select(
        study, sub_id, measurement_id,
        opt1_id = from,
        endpoint_id = to,
        opt1_sr = sr_value
      )
  ) %>%
  left_join(
    ppc_sr_matrix %>%
      select(
        study, sub_id, measurement_id,
        opt2_id = from,
        endpoint_id = to,
        opt2_sr = sr_value,
        sr_gamma, softmax_temperature, lapse_rate
      )
  ) %>%
  rowwise() %>%
  mutate(
    p_sr_opt1 = softmax(
      option_values = c(opt1_sr, opt2_sr) * 100,
      option_chosen = 1,
      temperature = softmax_temperature,
      use_inverse_temperature = TRUE,
      lapse_rate = lapse_rate
    )
  ) %>%
  group_by(
    measurement_id, shortest_path, startpoint_id, endpoint_id, opt1_id, opt2_id
  ) %>%
  summarise(
    p_sr_opt1 = mean(p_sr_opt1, na.rm = TRUE),
    .groups = "drop"
  )
```

## Plots

This plot shows predicted behavior before and after overnight rest. All agents (human, SR, BFS) show similar patterns of behavior across the two days.

```{r plot-ties-before-after-overnight-rest}
plot_ties_before_after_overnight_rest <- tie_item_analysis_humans %>%
  left_join(tie_item_analysis_bfs) %>%
  left_join(tie_item_analysis_sr) %>%
  pivot_longer(
    starts_with("p_"),
    names_to = "agent",
    values_to = "p_choose_opt1"
  ) %>%
  mutate(
    agent = str_remove_all(agent, "p_|_opt1"),
    agent = case_when(
      agent == "human" ~ "Human",
      agent == "sr" ~ "SR",
      agent == "bfs" ~ "BFS",
    ),
    agent = fct_relevel(agent, "Human", "SR")
  ) %>%
  ggplot(aes(x=shortest_path, y=p_choose_opt1, color=measurement_id)) +
  theme_custom() +
  facet_wrap(~agent) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_point(
    alpha = 0.25, position = position_dodge(width = 0.5), show.legend = FALSE
  ) +
  stat_summary(
    aes(group=measurement_id),
    geom = "crossbar", fun = mean,
    position = position_dodge(width = 0.5)
  ) +
  scale_x_discrete(name = "Shortest path distance") +
  scale_y_continuous(
    name = "p(Choose Source A > B)",
    labels = scales::percent, breaks = seq(0, 1, 0.25)
  ) +
  scale_color_manual(
    name = NULL,
    labels = c("D1"="Before overnight rest", "D2"="After overnight rest"),
    values = c("D1"="#7b3294", "D2"="#008837")
  ) +
  coord_cartesian(ylim = c(0.1, 0.8)) +
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom"
  ) +
  ggtitle(
    "Navigation problems with two correct answers",
    subtitle = "Before and after overnight rest"
  )

plot_ties_before_after_overnight_rest

if (knitting) {
  ggsave(
    here("figures", str_c("navigation_heldout_day1_to_day2", ".pdf")),
    plot = plot_ties_before_after_overnight_rest,
    width = 6, height = 4,
    units = "in", dpi = 300
  )
}
```

The BFS parameters tend to push predicted choice towards chance: the search threshold models an agent's tendency to 'give up' and choose randomly during long searches, and the lapse rate models irreducible decision noise resulting in random choice. Here, we examine whether an unfettered, asymptotic BFS agent does a better job of mirroring human choice.

```{r plot-ties-asymptotic-bfs}
plot_ties_asymptotic_bfs <- tie_item_analysis_humans %>%
  left_join(bfs_avg_accuracy_ties) %>%
  pivot_longer(
    starts_with("p_"),
    names_to = "agent",
    values_to = "p_choose_opt1"
  ) %>%
  mutate(
    agent = str_remove_all(agent, "p_|_opt1"),
    agent = case_when(
      agent == "human" ~ "Human",
      agent == "bfs" ~ "BFS",
    ),
    agent = fct_relevel(agent, "Human")
  ) %>%
  ggplot(aes(x=shortest_path, y=p_choose_opt1, color=measurement_id)) +
  theme_custom() +
  facet_wrap(~agent) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_point(
    alpha = 0.25, position = position_dodge(width = 0.5), show.legend = FALSE
  ) +
  stat_summary(
    aes(group=measurement_id),
    geom = "crossbar", fun = mean,
    position = position_dodge(width = 0.5)
  ) +
  scale_x_discrete(name = "Shortest path distance") +
  scale_y_continuous(
    name = "p(Choose Source A > B)",
    labels = scales::percent, breaks = seq(0, 1, 0.25)
  ) +
  scale_color_manual(
    name = NULL,
    labels = c("D1"="Before overnight rest", "D2"="After overnight rest"),
    values = c("D1"="#7b3294", "D2"="#008837")
  ) +
  coord_cartesian(ylim = c(0.1, 0.8)) +
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom"
  ) +
  ggtitle(
    "Navigation problems with two correct answers",
    subtitle = "Asymptotic BFS agent"
  )

plot_ties_asymptotic_bfs

if (knitting) {
  ggsave(
    here("figures", str_c("navigation_heldout_asymptotic_bfs", ".pdf")),
    plot = plot_ties_asymptotic_bfs,
    width = 4, height = 4,
    units = "in", dpi = 300
  )
}
```

